---
title: "playing with 2000-2002"
author: "Randy Swaty"
date: "11/24/2020"
output:
  html_document:
    number_sections: no
    theme: journal
    toc: yes
    toc_depth: 3
    toc_float:
      toc_collapsed: yes

---
<style>
body {
    font-family: Georgia,"Times New Roman",Times,serif;
    font-size: 15px;
    line-height: 1.42857143;
    color: #000000;
    background-color: #ffffff;
}
</style>
---


## The basics...

Laura Roncal wisely suggested we pilot processing of the ABRP data.  We discussed and decided to:

* divide and conquer, with Randy taking on the "Canopy" data, and Laura the "Pine" data.  After that we'd make a decision about the "herb" data
* start with 2000-2002 data
* I created a new Excel Workbook and :
    * made three sheets: data, headers (see note below) and notes
    * pasted all "metadata" from each year in the "headers" sheet
    * pasted data in chronological order in "data" sheet
    * visually inspected data and headers
    
    
## Notes 

* "headers" is not the best name...should be "legend" or "metadata"
* 



```{r}
library(tidyverse)
library(ggplot2)
```


```{r}
canopy2000_2002 <- read_csv("canopy2000-2002.csv")
View(canopy2000_2002)
```
